% Shree KRISHNAya Namaha
\documentclass{article}
\title{LocationSaver Android App - Versions log}
\author{Nagabhushan S N}
\usepackage[a4paper,margin=1in,footskip=0.25in]{geometry}
\usepackage{hyperref}
\hypersetup {
colorlinks = true,
linkcolor = black
}

\begin{document}
    \maketitle
    \tableofcontents
    \newpage


    \section{v1.0.0 (1)}\label{sec:1}
    \begin{itemize}
        \item Created App
        \begin{itemize}
            \item Name: Location Saver
            \item Package: com.chaturvedi.locationsaver
        \end{itemize}
        \item In MainActivity, saved locations will be displayed. On clicking, ``Complete Action Using" dialog will be displayed to open the location in Maps.
        \item 3 MenuItems added: `Export', `Import', `Add Location'.
        \item On clicking `Add Location', coordinates will be taken using GPS. A dialog is displayed which contains
        \begin{itemize}
            \item Name: To be entered
            \item Coordinates: Filled automatically
            \item Address: To be entered
            \item Notes: To be entered
        \end{itemize}
        \item On adding, location will be saved on SD Card: Internal/chaturvedi/LocationSaver/Locations.txt
    \end{itemize}


    \section{v1.0.1 (2)}\label{sec:2}
    \begin{itemize}
        \item On adding Location or cancelling, GPS searching was not stopped. Fixed.
        \item Location shared in WhatsApp when tried to open, among the apps in Chooser window, `Location Saver' appears. On selecting `Location Saver' will be opened with `Add Location' dialog displayed. Coordinates will be auto-filled using the data from WhatsApp.
        \item Bug: In app, on clicking a location, `Location Saver' will also be displayed among the options, leading to recursion.
        \item Other bug fixes.
    \end{itemize}


    \section{v1.0.2 (3)}\label{sec:3}
    \begin{itemize}
        \item Data will be saved in database rather than SD card
        \item Update01To03 class reads data from SD, saves it to database and deletes file in SD
        \item SplashActivity created (no splash screen for now). It just checks for app updates and if found, runs the corresponding Update classes and starts MainActivity.
    \end{itemize}


    \section{v1.0.3 (4)}\label{sec:4}
    \begin{itemize}
        \item Import and Export functionalities added.
        \item On Export, a `.txt' file will be saved in `Internal/Android/Chaturvedi/Location Saver' folder with name `Locations-YYYYMMDDhhmmss.txt'
        \item On Import, FileChooser will be opened to choose the file. On choosing, locations will be read and saved to database. In case the file is corrupted, possible locations will be read and a Toast text will be displayed.
    \end{itemize}


    \section{v1.0.4 (5)}\label{sec:5}
    \begin{itemize}
        \item Updated project to AndroidStudio 3.4
        \item minSdkVersion set to 21 (Lollipop)
        \item targetSdkVersion set to 28
        \item Location and Storage permissions will be requested at run time.
        \item Editing and deleting a location functionality added.
    \end{itemize}


    \section{v1.0.5 (6)}\label{sec:6}
    \begin{itemize}
        \item Package name changed from `\textit{com.chaturvedi.locationsaver}' to `\textit{com.krishna.nagabhushansn95.locationsaver}'
        \item App released to Google Play
    \end{itemize}


    \section{v1.0.6 (7)}\label{sec:7}
    \begin{itemize}
        \item Changed com.android.support to androidx.support.
        \item Some residual changes in project
    \end{itemize}


    \section{v1.0.7 (8)}\label{sec:8}
    \begin{itemize}
        \item
    \end{itemize}
\end{document}
